---
title: "Salaries of Heads of State - App Pitch"
author: "José Eduardo Mata"
date: "12/16/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Salaries of Heads of State, the app!

Curious about how much your a*¡&ole, I mean commander in chief is making? 

Would you like to compare his/her salary with those of other countries leaders? 

How about visualizing this information on an interactive map?

Your prayers have been answered!

##Look no further! 
Check out the protoype at: 
https://jeduardomata.shinyapps.io/Anual_Salaries_of_Heads_of_State_in_USD_MAP/

It's simple: Just toggle the slider and see which countries' leaders make that kind of money anually. Click on a highlighted country and see the details. YEEEES!

## Features
- Choose the range of salaries and see the map react
- Press on a country and see information

That's about it! But support our app and we promise new features, such as:

- Toggle between heads of state and heads of government
- Visualize salaries divided by GDP per capita, and other indicators. You will be surpirsed!
- More information about these scoundrils, their incomes and the countries.

## The history

A significant piece of this app came from me tryig to make a chloropeth map with the data. I really wanted to learn to use polygons, I finally managed.

```{r, echo = FALSE, warning=FALSE, message=FALSE, results=TRUE}
library(leaflet)
library(readr)
library(geojsonio)
library(RColorBrewer)
library(sp)

Data <- read_csv("data.csv")
countries <- geojson_read("json/simplecountries.geojson", what = "sp")
m <- leaflet() %>%
  addTiles%>%
  addPolygons(data = countries, weight = .5)
countries <- merge(countries, Data, by = "iso3")

bins <- c(0, 16639, 33809, 56529, 74594, 104999, 194299, 809672, Inf)
pal <- colorBin("YlOrRd", domain = countries$head_of_state_salary_usd, bins = bins)

options(scipen=999)

m %>% addPolygons(data = countries,
  fillColor = ~pal(head_of_state_salary_usd),
  weight = .5,
  opacity = 1,
  color = "white",
  fillOpacity = 0.7,
  popup = paste(countries$state, countries$post, prettyNum(countries$head_of_state_salary_usd, big.mark = ",", drop0trailing = FALSE), sep = " - ")) %>% setView(40.433333, -3.7, zoom = 1)

```

## An interesting variation 

Salaries divided by the countries' GDP per capita. (I'd like to incoproprate this into the app at some point).

```{r, echo = FALSE, warning=FALSE, message=FALSE, results=TRUE}
bins <- c(0, 4, 5.47, 8.30, 12.12, 21.08, 39.14, 124.65, Inf)
pal <- colorBin("YlOrRd", domain = countries$head_of_state_salary_divided_by_gdp_per_capita, bins = bins)

m %>% addPolygons(data = countries,
  fillColor = ~pal(head_of_state_salary_divided_by_gdp_per_capita),
  weight = .5,
  opacity = 1,
  color = "white",
  fillOpacity = 0.7,
  popup = paste(countries$state, countries$post,     prettyNum(countries$head_of_state_salary_divided_by_gdp_per_capita, big.mark = ","), sep = " - ")) %>% setView(40.433333, -3.7, zoom = 1)
```

